---
title: "Paitent-Tracking"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/salma/OneDrive/Desktop/PaitentTracking")
library(MCMCpack)
source("functions.R")
source("basic_dataset.R")
source("first_Iteration_function.R")
source("after_First_Iteration_functions.R")
```

## Set up dataset

Make a matrix with 20 rows 19 columns
Randomly select 0.2 and set NA of to them


```{r}
psiLast<-0
psiNew <-0
iteration <- 1
mat<- getMainDataSet()
indexSet <- getMissingIndex(mat)
mat      <- omitEnteries(mat,indexSet)
```

Obtain the first psi matrix and get the chance matrix of it

```{r}
psiNew<- createTransitionMatrix(mat)
chanceMatrix<-obtainChanceMatrix(psiNew)
```

Fill the NAs with a proper prediction

```{r}
mat<-fillNA_First_Iteration(mat,chanceMatrix,indexSet )  
```

 1. Update a the Psi
 2. Compare the new psi with the previous iteration psi
 3. As long as the 2 last psi matrices are not converged do the following
 
   3.1. Fill the missed enteries
 
   3.2. Update the psi
 
   3.3. Back to 3

Continue until the difference between the 2 last psi become less than 0.02

```{r}
while(!isPSIsConverged(psiNew,psiLast,0.015)){     
                              #if it is not cpnverged then continue until convergance
   
   psiLast <-psiNew                      # Store the previous Psi matrix
   psiNew<-createTransitionMatrix(mat)   # Get a new Psi
    
  
  mat <- fillNA_After_First_Iteration(mat,psiNew, indexSet )
  
  
  iteration<- iteration+1
  printData(iteration)

}

psiLast
psiNew
```





